\documentclass[../main.tex]{subfiles}

\begin{document}

\chapter{Pilot Design and Results}

This chapter details the process of development of the experimental design,
through the execution of several pilot experiments. First, the initial design
(based from \citeauthor{Fastl1982Fluctuation} study~\cite{Fastl1982Fluctuation})
is presented. Then, the iterative process of the pilots execution is detailed,
stating the progressive changes made to the initial design. Finally, a series of
conclusions that lead to the final experimental design are presented.

\section{Design}

\subsection{Equipment}
\label{subsec:pilot_equipment}

A personal computer with an audio interface M-Audio Transit and a set of
headphones Sennheiser HD 265 Linear were used to conduct the experiment. The
computer was positioned in a sound-isolated booth. The experiment itself was
programmed using the APEX software platform and Windows batch files.

\subsection{Methods}

The experiment is divided in two phases:
\begin{inparaenum}[(1)]
  \item the training phase (\ref{subsub:training_phase});
  \item and the experimental phase (\ref{subsub:experimental_phase}).
\end{inparaenum}

\subsubsection{Training phase}
\label{subsub:training_phase}

The objective of this phase is to make clear the concept of fluctuation strength
to the participants. First, a subset of \gls{AM} tones
(\cref{tab:initial_am_training_stimuli}) is presented to the participants
sequentially according to their id in pairs, while being asked whether a
difference in the fluctuation strength among stimuli is detected.

\begin{table}[!ht]
  \centering
  \begin{tabu}{l l l l l}
    \toprule
    \rowfont\bfseries
    Id & $\bm{f_m}$ [Hz] & $\bm{f_c}$ [kHz] & SPL [dB] & $\bm{m_d}$ [dB] \\
    \midrule
    1 & 0   & 1 & 70 & 40 \\
    \midrule
    2 & 0.5 & 1 & 70 & 40 \\
    \midrule
    3 & 4   & 1 & 70 & 40 \\
    \midrule
    4 & 32  & 1 & 70 & 40 \\
    \bottomrule
  \end{tabu}
  \caption{Initial subset of \gls{AM} stimuli for training phase}
\label{tab:initial_am_training_stimuli}
\end{table}

Afterwards, a longer stimulus composed several stimuli
(\cref{tab:initial_am_training_stimuli}), separated by 800 ms of silence, is
presented to the participants. This to expose them to a wider range of stimuli
and thus familiarize them to them.

\begin{table}[!ht]
  \centering
  \begin{tabu}{l l l l l}
    \toprule
    \rowfont\bfseries
    Order & $\bm{f_m}$ [Hz] & $\bm{f_c}$ [kHz] & SPL [dB] & $\bm{m_d}$ [dB] \\
    \midrule
    1 & 8    & 1 & 70 & 40 \\
    \midrule
    2 & 0.5  & 1 & 70 & 40 \\
    \midrule
    3 & 0    & 1 & 70 & 40 \\
    \midrule
    4 & 2    & 1 & 70 & 40 \\
    \midrule
    5 & 32   & 1 & 70 & 40 \\
    \midrule
    6 & 4    & 1 & 70 & 40 \\
    \midrule
    7 & 16   & 1 & 70 & 40 \\
    \midrule
    8 & 1    & 1 & 70 & 40 \\
    \midrule
    9 & 0.25 & 1 & 70 & 40 \\
    \bottomrule
  \end{tabu}
  \caption{Initial longer stimulus composed of \gls{AM} stimuli for training
  phase}
\label{tab:initial_am_all_stimulus}
\end{table}

\subsubsection{Experimental phase}
\label{subsub:experimental_phase}

A magnitude estimation procedure was used to obtain the relative fluctuation
strength as a function of a varying parameter for the two types of tones. There
were four different parametric variations:
\begin{inparaenum}[(1)]
  \item \gls{f_m};
  \item \gls{f_c};
  \item \gls{SPL};
  \item \gls{m_d} for \gls{AM} tones, \gls{d_f} for \gls{FM} tones.
\end{inparaenum}
Each of these parameters defined an experiment section on its own.

Each magnitude estimation presented pairs of sounds, composed of one of two
possible standards (\cref{tab:standards}) and a stimulus from the section set.
The standard and the stimulus are separated by a 800 ms silence. There were four
repetitions per pair, and hence eight per stimulus. The selection of the
standard and the stimulus used is randomized.

\begin{table}[!ht]
  \centering
  \begin{tabu}{l l l l l l}
    \toprule
    \rowfont\bfseries
    \multirow{2}{*}{Section} &
    \multicolumn{5}{c}{Parameters} \\
    \cmidrule{2-6}
    \rowfont\bfseries
    & $\bm{f_m}$ [Hz] & $\bm{f_c}$ [kHz] & SPL [dB] & $\bm{m_d}$ [dB] &
    $\bm{d_f}$ [Hz] \\
    \midrule
    \multirow{2}{*}{AM-fm}  & 4 & 1 & 70 & 40 & --- \\
                            & 0.25 & 1 & 70 & 40 & --- \\
    \midrule
    \multirow{2}{*}{AM-fc}  & 4 & 1 & 70 & 40 & --- \\
                            & 4 & 0.25 & 70 & 40 & --- \\
    \midrule
    \multirow{2}{*}{AM-SPL} & 4 & 1 & 70 & 40 & --- \\
                            & 4 & 1 & 50 & 40 & --- \\
    \midrule
    \multirow{2}{*}{AM-md}  & 4 & 1 & 70 & 40 & --- \\
                            & 4 & 1 & 70 & 4 & --- \\
    \midrule
    \multirow{2}{*}{FM-fm}  & 4 & 1.5 & 70 & --- & 700 \\
                            & 0.5 & 1.5 & 70 & --- & 700 \\
    \midrule
    \multirow{2}{*}{FM-fc}  & 4 & 6 & 70 & --- & 200 \\
                            & 4 & 0.5 & 70 & --- & 200 \\
    \midrule
    \multirow{2}{*}{FM-SPL} & 4 & 1.5 & 60 & --- & 700 \\
                            & 4 & 1.5 & 40 & --- & 700 \\
    \midrule
    \multirow{2}{*}{FM-df}  & 4 & 1.5 & 70 & --- & 700 \\
                            & 4 & 1.5 & 70 & --- & 32 \\
    \bottomrule
  \end{tabu}
  \caption{Description of the standards used per experiment section}
\label{tab:standards}
\end{table}

\subsection{Stimuli}
\label{subsec:pilot_stimuli}

All the sounds presented during the experiment consisted of diotic stimuli. Two
types of stimuli were considered: \gls{AM} tones, \cref{eq:am}; and \gls{FM}
tones, \cref{eq:fm}. In these equations, a $-\frac{\pi}{2}$ phase shift is
introduced to the modulating signal for both tones in order to start the
corresponding modulation at its lowest point. This phase shift is needed to
avoid pops and clicks due to an abrupt onset when presenting the sounds to the
participants. Additionally, a cosine ramp with attack and release times of 25 ms
was applied to the stimuli to further prevent this phenomenon.

\begin{equation}
  x_{am} = A_c \cdot [1 - m_d \cdot \cos(2 \pi f_m t)] \cdot \sin(2 \pi f_c t),
 \text{where } m_d = \frac{A_m}{A_c}
  \label{eq:am}
\end{equation}

\begin{equation}
  x_{fm} = A_c \cdot \sin \{2 \pi [f_c - d_f \cdot \cos(2 \pi f_m t)] t \}
  \label{eq:fm}
\end{equation}

The duration of the stimuli was specified such that it presented at least three
periods of the modulating signal, within a range of values between 2 and 4
seconds. Therefore, stimuli with long periods (e.g., $f_m$ = 0.25 Hz) were
truncated to 4 seconds and stimuli with short periods (e.g., $f_m$ = 32 Hz) were
generated to reach a 2 seconds duration. This was done to maintain a similar
duration among stimuli while keeping the whole experiment duration to an
acceptable value.

Furthermore, the stimuli were generated such that a 100 dB SPL value
corresponds to a 0 dBFS value.

\Cref{tab:initial_stimuli} presents all the stimuli used for the different
experimental sections, stating which parameters were fixed and which were varied.

\begin{table}[!ht]
  \centering
  \begin{tabu}{l p{3cm} l}
  \toprule
  \rowfont\bfseries
  \multirow{2}{*}{Section} &
  \multicolumn{2}{c}{Parameters} \\
  \cmidrule{2-3}
  \rowfont\bfseries
  & \multicolumn{1}{c}{Fixed} & \multicolumn{1}{c}{Varied} \\
  \midrule
  AM-fm  & $f_c$ = 1 [kHz]\par SPL = 70 [dB]\par $m_d$ = 40 [dB]
         & $f_m$ = \{0, 0.25, 0.5, 1, 2, 4, 8, 16, 32\} [Hz] \\
  \midrule
  AM-fc  & $f_m$ = 4 [Hz]\par SPL = 70 [dB]\par $m_d$ = 40 [dB]
         & $f_c$ = \{0.125, 0.25, 0.5, 1, 2, 4, 8\} [kHz] \\
  \midrule
  AM-SPL & $f_m$ = 4 [Hz]\par $f_c$ = 1 [kHz]\par $m_d$ = 40 [dB]
         & SPL = \{50, 60, 70, 80, 90\} [dB] \\
  \midrule
  AM-md  & $f_m$ = 4 [Hz]\par $f_c$ = 1 [kHz]\par SPL = 70 [dB]
         & $m_d$ = \{1, 2, 4, 10, 20, 40\} [dB] \\
  \midrule
  FM-fm  & $f_c$ = 1.5 [kHz]\par SPL = 70 [dB]\par $d_f$ = 700 [Hz]
         & $f_m$ = \{0, 0.25, 0.5, 1, 2, 4, 8, 16, 32\} [Hz] \\
  \midrule
  FM-fc  & $f_m$ = 4 [Hz]\par SPL = 70 [dB]\par $d_f$ = 200 [Hz]
         & $f_c$ = \{0.5, 1, 1.5, 2, 3, 4, 6, 8\} [kHz] \\
  \midrule
  FM-SPL & $f_m$ = 4 [Hz]\par $f_c$ = 1.5 [kHz]\par $d_f$ = 700 [Hz]
         & SPL = \{40, 50, 60, 70, 80\} [Hz] \\
  \midrule
  FM-df  & $f_m$ = 4 [Hz]\par $f_c$ = 1.5 [kHz]\par SPL = 70 [dB]
         & $d_f$ = \{16, 32, 100, 300, 700\} [Hz] \\
  \bottomrule
  \end{tabu}
  \caption{Description of initial set of stimuli used per experiment section}
\label{tab:initial_stimuli}
\end{table}

\section{Development}

They were in total 9 participants in the pilot experiments. Not all participants
were subjected to the same experimental conditions, and not all of them used the
same version of the experiments. \Cref{tab:partexpconver} presents the
conditions and version to which the participants were subjected.

\begin{table}[!ht]
  \centering
  \begin{tabu}{ l l l l }
    \toprule
    \rowfont\bfseries
    Participant & AM & FM & Version \\
    \midrule
    1 & All & All & 1 \\
		\midrule
    2 & All & None & 1 \\
		\midrule
    3 & All & None & 1 \\
		\midrule
    4 & All & None & 1 \\
		\midrule
    5 & \gls{f_m} & None & 2 \\
		\midrule
    6 & \gls{f_m} & None & 3 \\
		\midrule
    7 & None & \gls{f_m}, \gls{f_c} & 3 \\
		\midrule
    8 & None & All & 3 \\
		\midrule
    9 & None & All & 4 \\
    \bottomrule
  \end{tabu}
  \caption{Participants experimental conditions and versions}
\label{tab:partexpconver}
\end{table}

The experimental procedure was varied during the pilot experiment to accommodate
perceived errors during the realization of them. The first version of the
experiment yielded unsatisfactory results with regards to the relation between
fluctuation strength and modulation frequency (participants 2, 3 and 4). The
procedure was then modified, adding two more AM tones with modulation
frequencies of 64 and 128 Hz. The idea behind the addition of these two tones
was that, if participant have stimuli that are clearly rough, it would be easier
for them to distinguish between a fluctuating and a rough tone. Additionally,
FM tones were included in the training, since up to this point only AM tones
were used in the training phase This constitutes the second version of the
experiment.

Participant 5 was the only participant that was subjected to version 2 of the
experiment. Its results did not show any significant improvements with regard
to the confusion between fluctuation strength and roughness. However, by talking
to the participants it was discovered that the instructions during the training
phase were not clear enough, and this may have affected the results of the
experiment. Several participants associated the rate of change of the stimuli
(modulation frequency in this case) to a bigger fluctuation in the presented
sounds. As so, they tended to deem as highly fluctuating sounds that had a high
modulation frequency. Participants 4 and 5 explicitly stated that they were
counting the number of cycles in the stimuli, due to confusion on what to
answer.

Taking all these comments as feedback, version 3 of the experiment was
elaborated. In this version, explicit instructions regarding the rough tones
were given. It was indicated that the sensation of fluctuation was unrelated to
the apparent `speed' of the stimuli, and that the answers should be based on a
intuitive way, based on the arising sensation and not rationalizing it (for
instance by counting cycles). Using this approach participants were able to
understand better the fluctuation strength concept, some of them even coming
with analogies to the sensation itself (the sound of an ambulance alarm, the
sound of a washing machine).

The final version, number 4, of the experiment added a small test experiment
before starting the actual experiment sections. This was added as a suggestion
of participant 8, who indicated that although the training phase was effective
in making clear the fluctuation strength concept, it did not showed the
participant how to do the expected judgments using the magnitude estimation
procedure. Moreover, a latin square randomization approach was used, to
distribute possible learning effects of participants among the experimental
conditions.

\section{Results}

The following are the results of all the participants grouped together by
experiment. In the appendix the individual results can be found. In all the
following figures, the error bars indicate the interquartile range and the
marker indicate the median value.

\begin{pilotresults}

\myfigurequad%
  {AM-fm_all_standards}
  {AM-fc_all_standards}
  {AM-SPL_all_standards}
  {AM-md_all_standards}
  {
    \caption{Pilot results --- Relative fluctuation strength for AM tones}
    \label{fig:pilot_AM_all_comparison}
  }

\myfigurequad%
  {FM-fm_all_standards}
  {FM-fc_all_standards}
  {FM-SPL_all_standards}
  {FM-df_all_standards}
  {
    \caption{Pilot results --- Relative fluctuation strength for FM tones}
    \label{fig:pilot_FM_all_comparison}
  }

\end{pilotresults}

\section{Conclusions}

From the obtained data it can be concluded that the main problem when dealing
with the fluctuation strength perceptual attribute is its ambiguity and
confusion with the roughness perceptual attribute. The proposed training phase
was effective in clarifying the concept to participants, by adding stimuli with
a clear rough sensation, and by clearly instructing them on what the sensation
is about. It should be noted that only with regard to modulation frequency this
confusion arises, the other parameters do not present this particularity and as
so it was not necessary to adapt the experimental procedure with them.

\end{document}
