\documentclass[../main.tex]{subfiles}

\begin{document}

\chapter{Participants Sheet}
\label{chap:participants_sheet}

The following sections gathers the participants details and remarks obtained
after the execution of the experiment. In \cref{tab:participants_details}, a
value of 1 in the tones column correspond to AM tones condition, and a value of
2 corresponds to FM tones condition. Furthermore,
\cref{tab:experimental_sections_order} presents the relation between the
condition column and the order of the experimental sections.

\begin{table}[!ht]
  \centering
  \begin{tabu}{XXXXXXXX}
    \toprule
    \rowfont\bfseries
    ID & Tones & Condition & External & Age & Gender & Date & Time \\
    \midrule
    1 & 1 & 1 & N & 27 & F & 10-08-15 & 15:00 \\
    2 & 2 & 1 & N & 23 & F & 10-08-15 & 16:30 \\
    3 & 1 & 2 & N & 23 & F & 11-08-15 & 09:00 \\
    4 & 2 & 2 & Y & 27 & M & 13-08-15 & 09:00 \\
    5 & 1 & 3 & N & 28 & M & 13-08-15 & 10:30 \\
    6 & 2 & 3 & N & 26 & M & 17-08-15 & 10:30 \\
    7 & 1 & 4 & N & 26 & M & 17-08-15 & 12:00 \\
    9 & 1 & 1 & N & 22 & M & 17-08-15 & 15:00 \\
    10 & 2 & 1 & Y & 26 & M & 17-08-15 & 16:30 \\
    11 & 1 & 2 & N & 23 & M & 18-08-15 & 09:00 \\
    12 & 2 & 2 & N & 26 & M & 18-08-15 & 10:30 \\
    13 & 1 & 3 & Y & 26 & F & 18-08-15 & 12:00 \\
    14 & 2 & 3 & N & 27 & M & 20-08-15 & 11:00 \\
    15 & 1 & 4 & N & 27 & M & 20-08-15 & 16:30 \\
    16 & 2 & 4 & Y & 18 & F & 21-08-15 & 12:00 \\
    17 & 1 & 1 & Y & 23 & M & 21-08-15 & 16:30 \\
    18 & 2 & 1 & N & 24 & M & 24-08-15 & 14:30 \\
    19 & 1 & 2 & N & 19 & M & 24-08-15 & 16:30 \\
    20 & 2 & 2 & N & 27 & F & 25-08-15 & 10:30 \\
    21 & 1 & 3 & N & 23 & M & 25-08-15 & 14:00 \\
    22 & 2 & 3 & N & 29 & M & 26-08-15 & 10:30 \\
    23 & 1 & 4 & N & 25 & M & 26-08-15 & 15:00 \\
    24 & 2 & 4 & N & 31 & M & 27-08-15 & 11:00 \\
    \bottomrule
  \end{tabu}
  \caption{Participants details}
\label{tab:participants_details}
\end{table}

\begin{longtabu} to \linewidth{lX}
  \toprule
  \rowfont\bfseries
  ID & Remarks \\
  \endhead
    \midrule
    1 & None \\
    \midrule
    2 & Participant coimplained that the experiment was long. She found the
    progress bar was distracting \\
    \midrule
    3 & Participant stated that in the last section of the experiment she was
    sleepy \\
    \midrule
    4 & Participant seemed to have some issues with the interface, during the
    test runs made a couple of mistakes \\
    \midrule
    5 & Participant recommended improvements to UI, more specifically to reset
    the slider after each trial \\
    \midrule
    6 & During the experiment, the participant asked if the sound intensity was
    to be considered with regards to the fluctuation of the sounds. Later he
    stated that he felt confused about it and he was initially paying attention
    just to the frequency of the sounds \\
    \midrule
    7 & Participant stated that he was sleepy to the end of the experiment. Had
    a little difficulty with the sound pressure level part \\
    \midrule
    8 & None \\
    \midrule
    9 & Participant seemed to have some doubts with the difference between
    roughness and fluctuation strength. Probably the same when it comes to
    SPL.\@ Seemed that he didn’t care that much about the experiment \\
    \midrule
    10 & Participant had some difficulties with SPL and with frequency. Possible
    confusion between fluctuating and rough tones. Overall the participant felt
    confused between the actual experiment and the training phase. He wasn’t
    capable of not rationalizing his judgment \\
    \midrule
    11 & None \\
    \midrule
    12 & None \\
    \midrule
    13 & Participant stated that she was tired at the last part of the
    experiment. Also, she suggested to reset the slider to avoid possible
    biases \\
    \midrule
    14 & Participant stated that he had some confusion with SPL.\@ Also, he said
    that sometimes he would think about the frequency and the envelope of the
    signal, possibly due to knowledge of DSP.\@ He also recommended to add a
    longer test experiment phase \\
    \midrule
    15 & Participant had some difficulties between pure tones and extremely
    rough tones. Took longer that most participants, wasn’t able to finish on
    time \\
    \midrule
    16 & Participant was quite shy. Possible difficulties with SPL and roughness
    vs fluctuation strength \\
    \midrule
    17 & None \\
    \midrule
    18 & None \\
    \midrule
    19 & Participant arrived fifteen minutes late. It was very difficult to
    communicate with him, didn’t seem to speak proper English. Not sure whether
    he understood correctly the concept of fluctuation strength. The participant
    wasn’t able to finish on time \\
    \midrule
    20 & Participant stated that the slider was difficult to use \\
    \midrule
    21 & None \\
    \midrule
    22 & Participant has quite impulsive and sometimes wouldn’t listen to
    instructions. He would answer contradictory sometimes. Took a little bit
    longer than most participant to complete the experiment. Not sure if he
    understood correctly the concept \\
    \midrule
    23 & None \\
    \midrule
    24 & Participant stated that at the third section he started to feel quite
    tired \\
    \bottomrule
    \caption{Participants remarks}
\end{longtabu}

\begin{table}[!ht]
  \centering
  \begin{tabu} to \linewidth{XX}
    \toprule
    \rowfont\bfseries
    Condition & Order \\
    \midrule
    1 & \gls{f_m}, \gls{f_c}, \{\gls{m_d} or \gls{d_f}\}, \gls{f_m}, \gls{SPL}\\
    2 & \gls{f_c}, \{\gls{m_d} or \gls{d_f}\}, \gls{f_m}, \gls{SPL}, \gls{f_m}\\
    3 & \{\gls{m_d} or \gls{d_f}\}, \gls{f_m}, \gls{SPL}, \gls{f_m}, \gls{f_c}\\
    4 & \gls{SPL}, \gls{f_m}, \gls{f_c}, \{\gls{m_d} or \gls{d_f}\}, \gls{f_m}\\
    \bottomrule
  \end{tabu}
  \caption{Experimental sections order according to condition}
\label{tab:experimental_sections_order}
\end{table}

\end{document}
